Exploring and Validating the Motives Behind API Evolution: A Case Study

### 2015-03-20 rmtw/a6/latex8.tex
analysis

A double inspection and a single joint inspection were used to collect the information from the APIs code and the documentation. This was performed to reduce research bias and human error. As part of the collection phase, the data were input into tables and spreadsheets, according to the API version.

@@

\subsection{Data Analysis}
• method for analysing the data (grounded theory? Thematic analysis? Statistical analysis?) strategies for validating findings

The interviews also provided us with more insight about the end users of the system. Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.

\subsection{Validity Threats}
This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.

%Internal Validity
\textit{Internal Validity} threats for our study have been greatly reduced by the methodologies we have employed. By performing a dual inspection and then a joint inspection of both the API source code, documentation and results analysis, \textit{internal validity} is significantly reduced. Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.

%External Validity
Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk. In our study we have striven to ensure that our findings will be as useful as possible to others. Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future. Our results come from both APIs either in production or soon to be in production. As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others. Likewise, other companies in similar positions could use the results of our study when creating their own APIs.

%Reliability
The largest \textit{reliability} threat facing our study was the reproducibility. To counter this threat, we have provided a clear and concise coding method for the collected data. Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible. To ensure clarity of the questions, we have field tested the interview with some of our peers, altering the questions based on their feedback.

[!!!Note to Richard \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]

>>>>

To reduce risks of research bias and human error, the data collection was performed by both researchers individually and indepenedtly. If the data differed, the cause was investigated and resolved. As part of the collection phase, the data were input into tables and spreadsheets, according to the API version.

@@

\subsection{Data Analysis}
The data analysis was conducted in two major phases \cite{andersson2007spiral}. During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study. It was during this phase that the analysis of the API code and documentation was carried out. The second phase included analysis of the interviews, the goal of it was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.

Both phases were performed iteratively, together with the data collection. The reason for this create the opportunity of being able to improve the process of analysis as the study progressed, as well as to be able to adapt to possible changes in direction due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.

The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}. More specifically, the approach undertaken was divided into three steps where the data first was coded based on which category of maintenance \cite{iso} the motive of the change corresponded with. Secondly, the codes were analysed from a high-level point of view, and the main goal was to identify trends in the codes. The third step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.

Following the analysis of the archival data, the results of the interviews were analysed. The interviews were analysed using the same approach taken for the archival data. The results of this analysis was then compared and correlated with the results of the code analysis.

We took the same approach (roles/double stuff) as in the collection to reduce human rerror + reseach bias.

Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.
